Conversations in time: interactive visualization to explore structured temporal data

### 2020-08-02 tsibbletalk.Rmd
draft on as_shared_tsibble()

* Symbolic formula to express structural specifications among keyed units, using `/` and `*` from Wilkinson notation (10.2307/2346786) for nesting and crossing.
* Nesting variables generate hierarchical tree, hence `plotly_key_tree()`. Overview and navigation made easier.
* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (categorical linking)
* Lists of key values, and json
* R6 subclass of mutaframes `SharedData` from {crosstalk} with metadata attached
* Self-linking: a single data source

>>>>

The \pkg{tsibbletalk} package, inspired by the \CRANpkg{crosstalk} package, introduces a shared tsibble data structure to enable reactivity for temporal data (i.e. a `tsibble`). The `as_shared_tsibble()` function turns a tsibble to a mutable tsibble `SharedTsibbleData`, as an R6 subclass of `SharedData` from {crosstalk}. A *tsibble* data object holds a set of interrelated series, identified by the "key", in a data frame. When the "key" includes more than two variables, there can exist intrinsic structures in all combinations of variables: either nesting or crossing. (Add an example here)

The `spec` argument in the `as_shared_tsibble()` function takes a symbolic formula to allow users to specify structural combinations, using `/` and `*` adopted from Wilkinson notation (10.2307/2346786) for nesting and crossing respectively.

* Nesting variables generate hierarchical tree, hence `plotly_key_tree()`. Overview and navigation made easier.
* One-to-many linking: marking a single point of interest highlights all other points that share particular data values (categorical linking)
* Lists of key values, and json
* Self-linking: a single data source

### 2020-08-02 tsibbletalk.tex
draft on as_shared_tsibble()

\begin{itemize}
\tightlist
\item
  Symbolic formula to express structural specifications among keyed
  units, using \texttt{/} and \texttt{*} from Wilkinson notation
  (10.2307/2346786) for nesting and crossing.
\item
  Nesting variables generate hierarchical tree, hence
  \texttt{plotly\_key\_tree()}. Overview and navigation made easier.
\item
  One-to-many linking: marking a single point of interest highlights all
  other points that share particular data values (categorical linking)
\item
  Lists of key values, and json
\item
  R6 subclass of mutaframes \texttt{SharedData} from \{crosstalk\} with
  metadata attached
\item
  Self-linking: a single data source
\end{itemize}

>>>>

The \pkg{tsibbletalk} package, inspired by the \CRANpkg{crosstalk}
package, introduces a shared tsibble data structure to enable reactivity
for temporal data (i.e.~a \texttt{tsibble}). The
\texttt{as\_shared\_tsibble()} function turns a tsibble to a mutable
tsibble \texttt{SharedTsibbleData}, as an R6 subclass of
\texttt{SharedData} from \{crosstalk\}. A \emph{tsibble} data object
holds a set of interrelated series, identified by the ``key'', in a data
frame. When the ``key'' includes more than two variables, there can
exist intrinsic structures in all combinations of variables: either
nesting or crossing. (Add an example here)

The \texttt{spec} argument in the \texttt{as\_shared\_tsibble()}
function takes a symbolic formula to allow users to specify structural
combinations, using \texttt{/} and \texttt{*} adopted from Wilkinson
notation (10.2307/2346786) for nesting and crossing respectively.

\begin{itemize}
\tightlist
\item
  Nesting variables generate hierarchical tree, hence
  \texttt{plotly\_key\_tree()}. Overview and navigation made easier.
\item
  One-to-many linking: marking a single point of interest highlights all
  other points that share particular data values (categorical linking)
\item
  Lists of key values, and json
\item
  Self-linking: a single data source
\end{itemize}
